Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
adding footnote for Hspec.
Fix grammar issues

In BDD, all behavior should be documented, together with some testable
\emph{evidence} for that behavior.  Most existing BDD tools only use
\emph{code examples} as evidence for behavior.
Hspec, a BDD tool for Haskell inspired by RSpec, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

@@

Hspec is thus useful for code documentation but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest} coped with Haddock~\cite{haddock},
standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

>>>>

In BDD, all behavior should be documented, together with some testable
\emph{evidence} for that behavior.  Most existing BDD tools only use
\emph{code examples} as evidence for behavior.
Hspec\footnote{%
http://hackage.haskell.org/package/hspec},
a BDD tool for Haskell inspired by RSpec, supports
both code examples and \emph{properties} as evidence.
It can verify examples and test properties, and it can create an
informal specification document from that.

@@

Hspec is thus useful for code documentation but we observed that parts
of a specification can be useful as user documentation. We pay attention
to Python's Doctest~\cite{doctest} for this purpose.
Doctest is not commonly described as a BDD tool, but we think
it can be used for BDD.
There is a Haskell version of Doctest\footnote{%
http://hackage.haskell.org/package/doctest}.  It is integrated with with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.
